\section{Hyperparameters}
\label{app:hyperparams}

\begin{table}[h]
\centering
\caption{Shared hyperparameters across \baseline{}, \method{}, and
\methodfree{}.}
\begin{tabular}{ll}
\toprule
Parameter & Value \\
\midrule
Outlier fraction & 0.35\% (global top-$k$) \\
Calibration pairs & 128 (Spider track: 1360) \\
Max sequence length & 2048 \\
Feature threshold quantile & 0.95 (per-example, positive $\Delta a$) \\
Transcoder TopK & 128 (\method{} only) \\
Native feature basis & MLP intermediate, $d_{\text{mlp}}{=}14{,}336$ (\methodfree{}) \\
GPTQ & true-sequential, 128 samples \\
$\Delta W$ reference & RTN $b$-bit (ablation) / GPTQ corrupt (Spider) \\
\bottomrule
\end{tabular}
\end{table}

\section{Contrastive corruption schema}
\label{app:corruptions}
Spider: schema swaps, wrong-SQL completions. GSM8K: corrupted chain-of-thought
with wrong intermediate steps and final answer. MMLU: wrong answer-choice
completions under the same 5-shot prompt.
\todo{full schema table from data\_prep\_contrastive.py}

\section{Saliency-source ablation: arm definitions}
\label{app:arms}
All arms share the mask format, 0.35\% global top-$k$ budget, GPTQ, and
evaluation. \textbf{random}: uniform random scores. \textbf{weight}: $|W|$.
\textbf{magnitude}: $|W|\cdot|\Delta W_{\text{RTN-}b\text{bit}}|$.
\textbf{ce}: $|W|\cdot|\Delta W|\cdot g_{\text{CE}}$. \textbf{align} /
\textbf{align$_{\text{free}}$}: $|W|\cdot|\Delta W|\cdot g_{\text{align}}$ in
the transcoder / native basis. \textbf{mult} / \textbf{mult$_{\text{free}}$}:
Eq.~\ref{eq:mult} in the transcoder / native basis.

\section{Transcoder-native feature audit}
\label{app:audit}
Per-layer task-feature density (\texttt{meta.layer\_feature\_density}) peaks in
mid layers 4--14, consistent with the layer-wise weight disagreement
(\S\ref{sec:analysis-overlap}). Top-K feature ranking by cumulative
clean$-$corrupt activation $\Delta a$ and manual labeling templates are
shipped with the code. \todo{populate manual labels}

\section{Additional results}
\label{app:additional}
\todo{Full Spider difficulty breakdown; complete dispute-sweep 2-bit row;
RTN vs.\ GPTQ $\Delta W$ ablation; cross-seed Jaccard tables.}

\section{Broader impact}
\label{app:impact}
Compression lowers the cost of deploying capable LLMs, which is dual-use in
the usual ways. Our interpretability-guided selection does not introduce new
capability risks beyond standard PTQ; it may improve auditability by making
the protected task circuit explicit.
