\section{Conclusion}
\label{sec:conclusion}

Low-bit PTQ forces a choice about which tiny fraction of weights must remain
in full precision. We started from an interpretability-guided answer---route
saliency through sparse transcoder features and intersect with the task loss
(\method{})---which beats \baseline{} at matched budget. Dissecting it with a
controlled ablation revealed the general principle underneath: protect a
weight only if it is salient to the task loss \emph{and} to the activation
circuit separating clean from corrupted task inputs, where the circuit can be
defined in the model's \emph{own} feature basis (\methodfree{}).

\paragraph{Three takeaways.}
\textbf{(1) The conjunction is the active ingredient.} In a controlled
saliency-source ablation with everything matched except the ranking signal,
the conjunction beats loss-only (CE/\baseline{}) and circuit-only selection on
both GSM8K and MMLU-STEM at 2-bit, and all circuit-informed arms dominate
magnitude/error/random controls by 10--26 points.
\textbf{(2) No dictionary required.} Computing the circuit term in the model's
own MLP-neuron basis (\methodfree{}) recovers most of the transcoder variant's
gain on GSM8K and surpasses it on MMLU-STEM---turning task-circuit PTQ from a
method gated on interpretability artifact releases into one that applies to
any transformer out-of-the-box.
\textbf{(3) Low-bit is where saliency matters.} At 3-bit all task-conditioned
methods converge to within seed noise; at 2-bit the saliency source separates
collapse from function. Mixed-precision PTQ research should therefore be
evaluated---and ablated---at the bit-widths where selection actually binds.

On Spider, intersecting CE with transcoder task-circuit attribution selects a
markedly different circuit ($J{=}0.30$ vs.\ \baseline{}) and improves 2-bit
execution accuracy by $+2.9$ points on average at matched budget, with causal
knockout supporting that the selected subnetwork implements task routing.

\paragraph{Future work.} Multi-task overlay masks
(\S\ref{sec:systems-outlook}), paired-bootstrap significance on all headline
gaps, second-model replication of the basis--task interaction, and
budget-fraction sweeps locating where the conjunction's advantage emerges.

\paragraph{Reproducibility.} Code, masks, contrastive calibration sets, and
replication logs: \todo{anonymous repo URL for submission}.
