\section{Results}
\label{sec:results}

We present results in the order of the paper's narrative: first, the
transcoder-guided method (\method{}) beats \baseline{} at matched budget
(\S\ref{sec:results-spider}, \S\ref{sec:results-downstream}); second, a
controlled ablation dissects \emph{why}, revealing the conjunction as the
active ingredient and the dictionary as optional (\S\ref{sec:ablation});
third, the bit-width analysis locates where any of this matters
(\S\ref{sec:results-3bit}).

\subsection{Spider text-to-SQL (primary head-to-head)}
\label{sec:results-spider}

Table~\ref{tab:spider} reports execution accuracy on the Spider dev set (1034
examples, test-suite-sql-eval) under the matched protocol. \method{} averages
29.4\% over four paired calibration seeds vs.\ \baseline{} 26.5\%
($+2.9$\,pp mean paired $\Delta$); the best seed reaches 32.6\%. Replacing CE
entirely with transcoder alignment (the circuit-only arm) ties \baseline{}
(25.0 vs.\ 26.0)---a
first hint, confirmed by the ablation below, that the improvement requires the
\emph{conjunction}, not the transcoder signal alone. At 3-bit, \baseline{}
reaches 64.8\%, circuit-only ties (65.0\%), and \method{} reaches 66.2\%
(seed 0)---again a compressed gap at the milder bit-width.

\begin{table}[t]
\centering
\caption{Spider execution accuracy (\%) on Llama-3.1-8B-Instruct, 0.35\%
budget, 1360 Spider-train contrastive calibration pairs. Multi-seed: mean $\pm$
sample std over four calibration seeds.}
\label{tab:spider}
\begin{tabular}{lcc}
\toprule
Method & FP16 & 2-bit \\
\midrule
FP16 (unquantized)          & 67.8 & --   \\
\baseline{}~\citep{xiao2025tacq} (mean) & -- & 26.5 $\pm$ 2.0 \\
circuit-only (transcoder, no CE) & -- & 25.0 \\
\method{} (mean)            & --   & \textbf{29.4 $\pm$ 2.7} \\
\method{} (best seed)       & --   & 32.6 \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Replication sanity check (Llama-3-8B).}
Our harness reproduces \baseline{} Spider exec accuracy: 67.7 (FP16), 22.3
(2-bit), 60.1 (3-bit) vs.\ paper 67.6 / 21.92 / 58.32~\citep{xiao2025tacq}.

\subsection{Task-conditioned downstream comparison (multi-seed)}
\label{sec:results-downstream}

Tables~\ref{tab:downstream2} and \ref{tab:downstream3} report the firm
head-to-head between \baseline{} and \method{} under the
task-conditioned protocol (calibrate and evaluate on the same task;
\S\ref{sec:setup}), with seeds varying the contrastive calibration sample.

\begin{table}[t]
\centering
\caption{Task-conditioned \textbf{2-bit} (0.35\% budget): mean over calibration
seeds $\{0,1,2\}$. GSM8K: 8-shot CoT accuracy; MMLU: held-out last 25\% of
test.}
\label{tab:downstream2}
\begin{tabular}{lcccc}
\toprule
Task & FP16 & \baseline{} & \method{} & \methodfree{} \\
\midrule
GSM8K                & 69.3 & 29.4 & 26.5 & 21.9$^*$ \\
MMLU STEM            & 59.0 & 44.5 & 43.6 & 41.9 \\
MMLU humanities      & 66.0 & 51.1 & 44.7 & \todo{pending} \\
MMLU social sciences & 75.6 & 57.2 & 52.8 & 53.6 \\
\bottomrule
\end{tabular}

\vspace{2pt}
{\footnotesize $^*$s2 pending (2 seeds). \baseline{} = TaCQ firm; \method{}
= ATLAS-T; \methodfree{} = ATLAS-N (dict-free). Per-seed numbers in
Appendix~\ref{app:per-seed}.}
\end{table}

\begin{table}[t]
\centering
\caption{Task-conditioned \textbf{3-bit}: same protocol. \baseline{} and
\method{} over seeds $\{0,1,2\}$; \methodfree{} over seeds $\{0,1,2\}$. All
gaps are within seed spread: at 3-bit the methods are statistically tied.}
\label{tab:downstream3}
\begin{tabular}{lcccc}
\toprule
Task & FP16 & \baseline{} & \method{} & \methodfree{} \\
\midrule
GSM8K                & 69.3 & 63.7 & 61.4 & 57.9 \\
MMLU STEM            & 59.0 & 56.5 & 54.6 & 53.6 \\
MMLU humanities      & 66.0 & 63.0 & \todo{hfx} & \todo{hfx} \\
MMLU social sciences & 75.6 & 73.0 & 74.0 & 72.6 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Saliency-source ablation: what carries the gain?}
\label{sec:ablation}

Having established that \method{} beats \baseline{} at matched budget, we ask
\emph{which ingredient does the work}. The ablation holds \emph{everything}
fixed---model (Llama-3.1-8B-Instruct), FP16 budget (0.35\%, global top-$k$),
contrastive calibration pairs (128), GPTQ (true-sequential), and
evaluation---and varies only the saliency signal that ranks weights. Eight
arms span the hypothesis space from task-agnostic controls to the full
conjunction, with each circuit arm instantiated in both the transcoder basis
and the model's native MLP-neuron basis (Table~\ref{tab:ablation}).

\begin{table}[t]
\centering
\caption{Saliency-source ablation at \textbf{2-bit} (0.35\% FP16 budget, seed 0).
Identical pipeline in every row; only the weight-ranking signal differs.
GSM8K: 8-shot CoT accuracy. MMLU splits: 5-shot accuracy on the held-out last
25\% of each subject's test split (chance $=25\%$).
Dict.\ = requires an external feature dictionary.}
\label{tab:ablation}
\small
\begin{tabular}{llccccc}
\toprule
Arm & Saliency signal & Dict. & GSM8K & STEM & Hum & Soc \\
\midrule
random    & uniform random                          & --  & 2.5  & 30.3 & 25.4 & 25.4 \\
weight    & $|W|$                                   & --  & 14.4 & 33.6 & 33.9 & 38.7 \\
magnitude & $|W| \cdot |\Delta W_{\text{quant}}|$   & --  & 16.7 & 27.8 & 25.7 & 31.5 \\
\midrule
ce ($\approx$\baseline{}) & CE gradient saliency    & --  & 25.4 & 41.3 & 44.2 & 54.1 \\
align        & circuit, transcoder basis            & \checkmark & 25.6 & 39.2 & 42.2 & 49.0 \\
align$_{\text{free}}$ & circuit, native basis       & --  & 22.9 & 42.6 & 45.7 & 52.6 \\
\midrule
mult (\method{})            & CE $\cap$ circuit, transcoder & \checkmark & \textbf{28.7} & 38.9 & 45.0 & 53.4 \\
mult$_{\text{free}}$ (\methodfree{}) & CE $\cap$ circuit, native & -- & 26.5 & \textbf{44.2} & \textbf{45.9} & \textbf{55.9} \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Finding 1: task-circuit information dominates bit-placement
heuristics.} Across all four tasks, every circuit-informed arm beats every
control by a wide margin. On GSM8K, magnitude selection recovers only 14.4\%
and magnitude$\times$error 16.7\%, versus 22.9--28.7\% for circuit-informed
selection; random placement collapses to 2.5\%. On MMLU the controls sit near
chance (25--39\%) while circuit arms reach 38.9--55.9\%. \emph{Where} the task
circuit lives carries most of the recoverable signal at 2-bit.

\paragraph{Finding 2: the conjunction is the active ingredient.}
On GSM8K the conjunction beats both of its parts: mult 28.7\% vs.\ ce 25.4\%
(loss-only) and align 25.6\% (circuit-only); paired bootstrap $p{=}0.005$ for
\method{} vs.\ \baseline{}. On MMLU-STEM the same holds in the native basis:
mult$_{\text{free}}$ 44.2\% vs.\ ce 41.3\% and align$_{\text{free}}$ 42.6\%
($p{=}0.022$ for \methodfree{} vs.\ \method{}, subject-cluster bootstrap).
On MMLU social sciences, \methodfree{} again leads (55.9 vs.\ ce 54.1 vs.\
align$_{\text{free}}$ 52.6). Neither signal alone suffices; the AND-gate over
task loss and task circuit is what buys accuracy. This retroactively explains
the Spider circuit-only result (\S\ref{sec:results-spider}): align-only tied
\baseline{} because it had discarded the loss half of the conjunction.

\paragraph{Finding 3: the dictionary is optional---and sometimes harmful.}
\methodfree{} recovers 92\% of the transcoder conjunction on GSM8K (26.5 vs.\
28.7) and \emph{surpasses every transcoder arm} on MMLU-STEM (44.2 vs.\ 38.9
for mult). We attribute the reversal to basis--task fit: the CRV transcoders
were trained to reconstruct general instruct-model behavior, and their feature
space may tile math-word-problem structure (GSM8K) better than the
heterogeneous knowledge retrieval MMLU requires; the native neuron basis is
task-neutral. Practically, the external dictionary is an optional booster on
some tasks rather than a dependency: conjunctive task-circuit PTQ works
out-of-the-box on any transformer.

\subsection{Conjunctive saliency is a low-bit phenomenon}
\label{sec:results-3bit}

We run the same controlled ablation at 3-bit (Table~\ref{tab:ablation3b}).
The contrast with the 2-bit table is the paper's sharpest result.

\begin{table}[t]
\centering
\caption{Saliency-source ablation at \textbf{3-bit} (0.35\% FP16 budget,
seed 0). Same eight-arm protocol as Table~\ref{tab:ablation}; only the
bit-width changes.}
\label{tab:ablation3b}
\small
\begin{tabular}{llcccc}
\toprule
Arm & Saliency signal & GSM8K & STEM & Hum & Soc \\
\midrule
random    & uniform random        & 36.2 & 45.4 & 52.3 & 60.1 \\
weight    & $|W|$                 & \textbf{62.4} & 54.2 & 58.5 & 70.1 \\
magnitude & $|W| \cdot |\Delta W|$& 56.6 & 48.7 & 56.4 & 65.9 \\
\midrule
ce ($\approx$\baseline{}) & CE gradient  & 58.3 & 54.7 & 60.7 & 71.2 \\
align     & circuit, transcoder   & 59.0 & 54.5 & 62.0 & 72.1 \\
mult (\method{}) & CE $\cap$ circuit, transcoder & 60.9 & 54.2 & 62.2 & \textbf{74.2} \\
\bottomrule
\end{tabular}
\end{table}

At \textbf{2-bit} (Table~\ref{tab:ablation}), the saliency source decides
between collapse and function: the spread between conjunction and magnitude
controls is 10--26 points, and weight magnitude recovers only 14.4\% on GSM8K.
At \textbf{3-bit}, these gaps collapse: weight magnitude \emph{leads} on GSM8K
(62.4\% vs.\ mult 60.9\%), and all circuit arms cluster within 4 points on
every task. The mechanism is simple: 3-bit quantization noise is small enough
that GPTQ's column-wise error compensation absorbs most task damage regardless
of which 0.35\% of weights are protected. At 2-bit the noise is catastrophic
and the FP16 budget must land on weights that are simultaneously task-critical
and quantization-fragile---precisely what the conjunction selects.

\paragraph{The quantizer--saliency interaction.}
To verify that the gain is in the mask, not the quantizer, we replace GPTQ with
RTN (round-to-nearest: no calibration, no error compensation) while keeping the
same masks. At 2-bit RTN, \emph{every} mask---including our best---produces
0\% GSM8K accuracy and 22\% MMLU-STEM (uniform random chance). RTN's rounding
error at 2-bit is catastrophic and unredeemable: no outlier selection can help
because the 99.65\% of quantized weights are too noisy for the model to
function. This locates the saliency contribution precisely: it operates in the
window that GPTQ opens---between ``noise too mild for masks to matter'' (3-bit)
and ``noise too severe for anything to help'' (2-bit RTN).

\paragraph{A cautionary note on bit-width bookkeeping.}
During this study we found that an earlier run had silently built ``2-bit''
\method{} engines at 3 bits (a quantizer default overriding the pipeline
intent), producing implausibly strong 2-bit numbers ($\sim$62\% GSM8K) that a
matched-budget ablation immediately exposed ($28.7\%$). We recommend
controlled saliency-source ablations as standard practice for mixed-precision
PTQ papers: they are cheap, and they catch both bookkeeping errors and
overclaiming.

\paragraph{Dispute sweep (anchored union).}
The anchored-union construction (\S\ref{sec:method-anchored}) locks the
consensus core ($\sim$46\% of budget at 2-bit) and re-ranks only the XOR
dispute mass. The mask morph behaves as designed ($J$ vs.\ \baseline{} falls
from 0.708 to 0.462 as $\lambda$ goes 0 to 1). Partial Spider evals at 3-bit
peak at the \baseline{}-heavy endpoint ($\lambda{=}0$: 63.2\% vs.\ 59.9\% at
$\lambda{=}0.5$), consistent with milder quantization favoring load-bearing
MLP mass over routing-heavy circuit weights. \todo{complete 2-bit sweep.}
