\section{Theoretical Framing: Encoded--Used Gap Dissociation}
\label{sec:encoded-used}

We frame \method{} against \baseline{} as a \emph{targeted scalpel} vs.\ a \emph{global broadsword}.
Both preserve a tiny FP16 outlier budget under mixed-precision GPTQ; they differ in \emph{what signal
selects} those outliers.

\paragraph{The encoded--used ambiguity in \baseline{}.}
Cross-entropy on final logits conflates two roles of weights in text-to-SQL:
\begin{itemize}
  \item \textbf{Encoding:} weights that store schema syntax, SQL templates, and lexical priors
        (often active whenever SQL-like tokens appear).
  \item \textbf{Using:} weights on causal execution edges---routing that binds columns, applies
        aggregations, and composes structure for the \emph{current} question.
\end{itemize}
Because CE gradients flow through the full vocabulary, \baseline{}'s contrastive saliency still
 mixes encoding and use under a single polysemantic ranking~\citep{xiao2025tacq}.
At 0.35\% outliers, wasting budget on passive encoders directly costs execution accuracy on Spider.

\paragraph{Dissociation via $F_{\text{task}}$.}
\method{} selects transcoder features with $\Delta a = \mathrm{ReLU}(a_{\text{clean}} - a_{\text{corr}}) > \tau$
and builds $y^{\text{target}}$ only from this task set $F_{\text{task}}$.
Gradients therefore align with weights that implement \emph{contrastive, task-active} MLP directions,
not every pathway that lowers CE on SQL surface form.
We call this \textbf{encoded--used gap dissociation}: outliers target active routing momentum rather
than undifferentiated static memory.
\todo{Cite feature-level audit or layer analysis supporting dissociation.}

\paragraph{What we claim in v1 vs.\ systems extensions.}
\textbf{v1 (this paper):} same static mask, same quantizer, same budget as \baseline{}; test whether
dissociation improves Spider execution accuracy at 2--3 bits.
\textbf{Extensions (outlook, \S\ref{sec:systems-outlook}):} distinct sub-task masks, orthogonality
constraints, and KV-cache-preserving hot-swaps---architectural capabilities \baseline{}'s static
monolith cannot express.
