\documentclass{article}
\usepackage{iclr2025_conference}
\usepackage{times}
\usepackage{natbib}
\usepackage{booktabs}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{multirow}

% --- TODO marker -------------------------------------------------------------
\newcommand{\todo}[1]{\textcolor{red}{[TODO: #1]}}

% --- Method name macros ------------------------------------------------------
% ATLAS = AND-gated Task-circuit Loss-Aligned Saliency (the method family).
\newcommand{\family}{ATLAS}
\newcommand{\method}{ATLAS-T}     % transcoder feature basis (ex T-DSO v2 mult)
\newcommand{\methodfree}{ATLAS-N} % native MLP-neuron basis, dictionary-free
\newcommand{\baseline}{TaCQ}

\title{\family{}: AND-Gated Task-Circuit and Loss-Aligned Saliency\\
for Low-Bit LLM Quantization}

\author{Anonymous Authors\\
\texttt{anonymous@domain.edu}}

\begin{document}
\maketitle

\begin{abstract}
Low-bit post-training quantization (PTQ) compresses large language models but
often destroys task-specific capabilities when only a tiny fraction of weights
can remain in full precision. Task-Circuit Quantization (\baseline{}) selects
FP16 outlier weights using contrastive gradients on cross-entropy loss,
treating the model as a black box. We propose \family{} (\emph{AND-gated
Task-circuit Loss-Aligned Saliency}): protect a weight only if it is salient
both to the task loss and to the task circuit. Our first instantiation,
\method{}, attributes quantization sensitivity through sparse, approximately
monosemantic transcoder features and \emph{intersects} this circuit signal
with standard CE saliency. Under a fixed
0.35\% outlier budget matched to \baseline{} on Llama-3.1-8B-Instruct,
\method{} improves Spider text-to-SQL execution accuracy by +2.9 points on
average over four paired calibration seeds (29.4\% vs.\ 26.5\%) and GSM8K
2-bit accuracy from 25.4\% to 28.7\%. We then ask \emph{why} it works. A
controlled saliency-source ablation---everything matched, only the
weight-ranking signal varies across eight arms---dissects the method and
yields three findings: (i) task-circuit information dominates magnitude,
quantization-error, and random placement (by 10--26 points at 2-bit); (ii) the
\emph{conjunction} of task loss and task circuit beats either signal alone;
and (iii) the transcoder itself is \emph{not} the active ingredient. Replacing
it with the model's \emph{own MLP neurons} as the feature basis
(\methodfree{}) recovers most of the gain on GSM8K (26.5\%) and surpasses all
transcoder arms on MMLU-STEM (44.2\% vs.\ 38.9\%)---turning a method gated on
external interpretability artifacts into one that applies to any transformer
out-of-the-box. At 3-bit all task-conditioned methods converge, identifying
conjunctive saliency as a distinctly \emph{low-bit} phenomenon: where to spend
the FP16 budget matters most exactly when the budget is harshest.
\end{abstract}

\input{sections/introduction}
\input{sections/theoretical_framing}
\input{sections/research_questions}
\input{sections/related_work}
\input{sections/method}
\input{sections/experimental_setup}
\input{sections/results}
\input{sections/domain_shift}
\input{sections/analysis}
\input{sections/limitations}
\input{sections/systems_outlook}
\input{sections/conclusion}

\bibliographystyle{plainnat}
\bibliography{references}

\appendix
\input{sections/appendix}

\end{document}
